Seminarium TI 3700\\ Data Analysis on Twitter(working title)

### 2014-03-18 authorinstr_2.tex
Todo dingen
eerste aanpassingen

\title{Seminarium TI 3700\\ Data Analysis on Twitter: An Overview (working title)}
\author{A. Hambenne  \and
    O. Maas \and
    R. Oosterloo}
\date{}

@@

\subsubsection{Classification Features}
To classify users a set of features is needed to distinguish between users. In this section we will present a list of frequently used features to classify users.  
\\\\
\textbf{Linguistics}\\
Linguistics can say a lot about the interests of a user. To classify a user Prototipical Words(PW's) can be used.  \cite{userclasst} PW's are words that are more used by users in class $A$ than users in class $B$. In a twitter-context also Prototipical Hashtags can be used.
\\\\
\textbf{Interaction Profiles}\\
Users interaction profiles is a profile created by Makazhanov \& Raﬁei to capture interactions between users and other accounts. \cite{pol} An interaction is a retweet or a reply. Pennacchiotti \& Popescu also uses friend accounts as a measurement in interaction between users. \cite{usermachine}  A friend account of user $x$ is an account that is followed by user $x$.  %TODO read this over, second sentence unclear 
\\\\
\textbf{Tweeting Behavior}\\
Tweeting behavior is a set of characteristics which shows us the way a user interacts with Twitter. Things like the average number of messages, the number of replies and the number of friends seems a good quantifier for classification. According to Pennacchiotti \& Popescu these features are useful but not really discriminative. \cite{usermachine}
\\\\
\textbf{Profile}\\
Profile information can be helpful to classify a user, but it should be used with care due to the amount of fake, inconsistent or incorrect information. According to Pennacchiotti \& Popescu  80\% of the users provides a location and 48\% of the users provides a short bio. \cite{usermachine} Furthermore their were able to extract a gender for 80\% of the users, but with a very low accuracy. They also researched the profile picture/avatar of twitter users and found out that these pictures can often be misleading. 20\% of the found profile pictures was not the owner but another person such as a celebrity. \cite{usermachine}

@@

After the clustering a number of features is used to distinguish between event and non-event clusters. The following features are used by Becker et al. to identify an event cluster. \cite{eventident} 
\begin{itemize}
  \item Temporal: The characteristics of the volume over the time $T_e$ associated with an event. 
  \item Social: The interactions between users(e.g. retweets, replies and mentions) during events could differ from other activities. 
  \item Topical: Tweets about events tend to center more around one central topic. Furthermore messages in event clusters are more likely to share one or more event-specific key-terms.  
  \item Twitter-centric: Some activities behave like an event but are Twitter-centric.(e.g. Tweets like 'Goodmorning!') These activities need to be filtered. 
\end{itemize}

With this list of features two event-classifiers are trained using two different techniques. The first classifier is trained using the "WEKA tookit"\footnote{http://www.cs.waikato.ac.nz/ml/weka/}, in the second classifier the  Naive-Bayes technique is used. According to Becker et al. the first classifier outperforms the second classifier in the separation of event and non-event clusters. \cite{eventident}
\\\\
\textbf{Aligning Tweets with an Event} \\
On average thousands of tweets are sent every minute using Twitter(\footnote{https://blog.twitter.com/2013/new-tweets-per-second-record-and-how}) . One of the main challenges in Event Identification is the alignment of tweets with their respective event. Rowe \& Stankovic try to create an automated mapping solution for this problem using semantics. \cite{eventalign}

@@

%TODO misschien wat meer info over het semantic web toevoegen.
After this process  Rowe \& Stankovic \cite{eventalign} uses multiple techniques to align a tweet with the respective event. The first technique used by them is Feature Extraction. \cite{eventalign} Three feature sets are used:
\begin{itemize}
%TODO uitwerken
  \item Immediate Resource Leaves: Use only the URI which are most indicative of an event. This feature only uses literals and resources within the URI of an event. 
  \item 1-Step Resource Leaves: Use all literals and resources within 1 step from the URI of an event. 
  \item DBPedia Concepts: Also uses all the concepts from DBPedia 
\end{itemize}
After this a Feature Vector is composed, for tweets all stop words are removed from the bag of words a tweet is represented as. Furthermore all stopwords are removed and everything is normalized to lowercase. \cite{eventalign} Then a labeling function is used to label the event. 
\subsubsection{Usecase: Earthquake Detection}
In Sakaki et al. their paper a usecase for Event Identification is presented in the form of a earthquake detection system. \cite{earthq} They consider twitter users as sensors. If enough sensors are activated (Tweets sent by a user are classified as a tweet about an earthquake), it is likely that an earthquake is occurring.

>>>>

\title{Seminarium TI 3700\\ Data Analysis on Twitter(working title)}
\author{A. Hambenne  \and
    O. Maas \and
    R. Oosterloo}
\date{}

@@

\subsubsection{Classification Features}
To classify users a set of features is needed to distinguish between users. In this section we will present a list of frequently used features to classify users.  
\\\\
\textbf{Linguistics}\\
Linguistics can say a lot about the interests of a user. To classify a user Prototipical Words(PW's) can be used.  \cite{userclasst} PW's are words that are more used by users in class $A$ than users in class $B$. In a twitter-context also Prototipical Hashtags can be used.
\\\\
\textbf{Interaction Profiles}\\
Users interaction profiles is a profile created by Makazhanov \& Raﬁei to capture interactions between users and other accounts. \cite{pol} An interaction is a retweet or a reply. Pennacchiotti \& Popescu also uses friend accounts as a measurement in interaction between users. \cite{usermachine}  A friend account of user $x$ is an account that is followed by user $x$.  
\\\\
\textbf{Tweeting Behavior}\\
Tweeting behavior is a set of characteristics which shows us the way a user interacts with Twitter. Things like the average number of messages, the number of replies and the number of friends seems a good quantifier for classification. According to Pennacchiotti \& Popescu these features are useful but not really discriminative. \cite{usermachine}
\\\\
\textbf{Profile}\\
Profile information can be helpful to classify a user, but it should be used with care due to the amount of fake, inconsistent or incorrect information. According to Pennacchiotti \& Popescu  80\% of the users provides a location and 48\% of the users provides a short bio. \cite{usermachine} Furthermore their were able to extract a gender for 80\% of the users, but with a very low accuracy. They also researched the profile picture/avatar of twitter users and found out that these pictures can often be misleading. 20\% of the found profile pictures was not the owner but another person such as a celebrity. \cite{usermachine}

@@

After the clustering a number of features is used to distinguish between event and non-event clusters. The following features can be used to identify an event cluster. \cite{eventident} 
\begin{itemize}
  \item Temporal: The characteristics of the volume over the time $T_e$ associated with an event. 
  \item Social: The interactions between users(e.g. retweets, replies and mentions) during events could differ from other activities. 
  \item Topical: Tweets about events tend to center more around one central topic. Furthermore messages in event clusters are more likely to share one or more event-specific key-terms.  
  \item Twitter-centric: Some activities behave like an event but are Twitter-centric.(e.g. Tweets like 'Goodmorning!') These activities need to be filtered because a classifier might identify it as an event. 
\end{itemize}

With this list of features two event-classifiers are trained using two different techniques. The first classifier is trained using the "WEKA tookit"\footnote{http://www.cs.waikato.ac.nz/ml/weka/}, in the second classifier the  Naive-Bayes technique is used. The first classifier outperforms the second classifier in the separation of event and non-event clusters. \cite{eventident}
\\\\
\textbf{Aligning Tweets with an Event} \\
On average thousands of tweets are sent every minute using Twitter(\footnote{https://blog.twitter.com/2013/new-tweets-per-second-record-and-how}) . One of the main challenges in Event Identification is the alignment of tweets with their respective event. Rowe \& Stankovic try to create an automated mapping solution for this problem using semantics. \cite{eventalign}

@@

After this process multiple techniques are used to align a tweet with the respective event. The first technique used by them is Feature Extraction. \cite{eventalign} The following three featuresets are used:
\begin{itemize}

  \item Immediate Resource Leaves: Use only the URI which are most indicative of an event. This feature only uses literals and resources within the URI of an event. 
  \item 1-Step Resource Leaves: Use all literals and resources within 1 step from the URI of an event. 
  \item DBPedia Concepts: Also uses all the concepts from DBPedia 
\end{itemize}
After this a Feature Vector is composed, for tweets all stop words are removed from the bag of words a tweet is represented as. Furthermore all stopwords are removed and everything is normalized to lowercase. \cite{eventalign} Then a labeling function is used to label the event. 
\subsubsection{Usecase: Earthquake Detection}
In Sakaki et al. their paper a usecase for Event Identification is presented in the form of a earthquake detection system. \cite{earthq} They consider twitter users as sensors. If enough sensors are activated (Tweets sent by a user are classified as a tweet about an earthquake), it is likely that an earthquake is occurring.
